Timbral similarity between extended playing techniques: the next frontier in querying instrumental databases

### 2018-01-28 paper/lagrangeSpontaneousSimilarity2017.tex
comment on citing Castellengo for definitions of timbre

\vl{Cite Kostka, Materials and Techniques of Post Tonal Music, Routledge, 2016, chapter 11, on the musicology of instrumental playing techniques. #biblio}

>>>>

\vl{On the musicology of extended playing techniques, cite:
Kostka, S (2016). Materials and Techniques of Post Tonal Music, Routledge, 2016, chapter 11. #biblio}

\vl{On the two definitions of timbre, cite:
 Castellengo, M and D Dubois (2007). ?Timbre ou timbres? Propriété
du signal, de l?instrument, ou construction cognitive?? In: Cahiers
de la Société québécoise de recherche en musique 9, pp. 25?38
#biblio}
